Supplementary Material: District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-09-26 paper/supp_figs.tex
New model specification tables added

We extracted variables such as age, cluster and survey sampling weight from all male respondents in the surveys, alongside information related to circumcision (if available): self-reported circumcision status, age at circumcision, Who performed the circumcision (whether the individual was circumcised by a health worker/professional, traditional practioner, other or unknown) and Where did the circumcision take place (whether the individual was circumcised at a health facility, in the home of a health worker/professional, at home, at a ritual site, other or unknown). The age of the respondents was calculated using both the century-month-code (CMC) of birth and interview dates. When calculating the residence of the respondents e matched survey data to clusters with accompanying (masked) geo-coordinates in order to assign the primary sub-national unit (PSNU) for modelling purposes. However, geo-cordinates were not available in some surveys and therefore we were unable to allocate their PSNU directly. Instead, we matched survey data to the least granular areal unit declared by the survey (most often level 1 administrative boundaries). Circumcisions were classed as a medical male circumcision (MMC) or traditional male circumcision (TMC) based on how responses to both ‘Who performed the circumcision?’ and ‘Where did the circumcision take place?’. Table 2 shows how the classification of circumcision type follows from these responses. Respondents that did not have any information related to the type of circumcision were classified as having “unknown” male circumcision (MC) type. Survey respondents were excluded if they were missing any demographic information or had a missing circumcision status. Table 1 shows a summary of the circumcision-related information from each surveys, and includes the availability of the circumcision related questions from the survey as well as the sample sizes in each survey. % For 5 countries, namely Liberia, Senegal, Niger, Guinea, and the DR Congo, information on circumcision type was not available in any surveys. Therefore, only MC could be estimated in these countries, and no inferences about circumcision type, whether MMC or TMC, could be made.

>>>>

We extracted variables such as age, cluster and survey sampling weight from all male respondents in the surveys, alongside information related to circumcision (if available): self-reported circumcision status, age at circumcision, Who performed the circumcision (whether the individual was circumcised by a health worker/professional, traditional practitioner, other or unknown) and Where did the circumcision take place (whether the individual was circumcised at a health facility, in the home of a health worker/professional, at home, at a ritual site, other or unknown). The age of the respondents was calculated using both the century-month-code (CMC) of birth and interview dates. When calculating the residence of the respondents e matched survey data to clusters with accompanying (masked) geo-coordinates in order to assign the primary sub-national unit (PSNU) for modelling purposes. However, geo-cordinates were not available in some surveys and therefore we were unable to allocate their PSNU directly. Instead, we matched survey data to the least granular areal unit declared by the survey (most often level 1 administrative boundaries). Circumcisions were classed as a medical male circumcision (MMC) or traditional male circumcision (TMC) based on how responses to both ‘Who performed the circumcision?’ and ‘Where did the circumcision take place?’. Table 2 shows how the classification of circumcision type follows from these responses. Respondents that did not have any information related to the type of circumcision were classified as having “unknown” male circumcision (MC) type. Survey respondents were excluded if they were missing any demographic information or had a missing circumcision status. Table 1 shows a summary of the circumcision-related information from each surveys, and includes the availability of the circumcision related questions from the survey as well as the sample sizes in each survey. % For 5 countries, namely Liberia, Senegal, Niger, Guinea, and the DR Congo, information on circumcision type was not available in any surveys. Therefore, only MC could be estimated in these countries, and no inferences about circumcision type, whether MMC or TMC, could be made.
